Inequalities Witnessing Quantum Incompatibility in The Triangle Scenario

### 2016-11-10 documents/Archive/main.tex
Started work on slides for Brazil

% \usepackage{silence}
% \WarningFilter{revtex4-1}{Repair the float}
% \usepackage{algorithm}
% \usepackage[noend]{algpseudocode}
% === All of the Packages I use frequently ===
\usepackage{../packages/shared}

% === Drafting Declarations ===
\draftprofile[TC Fraser]{TC}{Red}
\draftprofile[Elie Wolfe]{E}{Green}

% === Numbering For amsthm theorem environments ===
\theoremstyle{plain}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}

\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem{example}[theorem]{Example}

\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}

% === To allow for labeling of rows and columns of a matrix ===
%\usepackage{kbordermatrix}
\usepackage{../packages/kbordermatrix}
\renewcommand{\kbldelim}{(} % Left delimiter
\renewcommand{\kbrdelim}{)} % Right delimiter

% === Commonly re-occurring symbols ===
\newcommand{\hgraph}{\mathcal{H}}
\newcommand{\graph}{\mathcal{G}}
\newcommand{\nodes}{\mathcal{N}}
\newcommand{\weights}{\mathcal{W}}
\newcommand{\edges}{\mathcal{E}}
\newcommand{\trans}{\mathcal{T}}
\newcommand{\ind}{S}
\newcommand{\inhibit}{\mathcal{I}}
\newcommand{\netperm}{\Pi}
\newcommand{\Hilb}{\mathcal{H}}
\newcommand{\ancestralindep}{\perp}
\newcommand{\valprod}{\times}
\newcommand{\bigvalprod}{\prod}
\newcommand{\com}{\mathrel{\Yright\hspace{-0.2em}\Yleft}}
\newcommand{\ext}{\mathrel{\Yleft}}
\newcommand{\res}{\mathrel{\Yright}}
\newcommand{\gep}{\varphi}
\newcommand{\gp}{\Phi}
\newcommand{\geo}{\omega}
\newcommand{\go}{\Omega}
\newcommand{\mscenario}{\mathcal{M}}
\newcommand{\jointvar}{\mathcal{J}}
% \newcommand{\mset}{\gamma}
% \newcommand{\extmset}{\Gamma}
\newcommand{\supp}[1]{\si\br{#1}}
\newcommand{\kone}{\mathbf{1}}
\newcommand{\kzer}{\textcolor{gray}{0}}

% \newcommand{\mext}[1]{E_{#1}}
% \newcommand{\mul}[1]{\Gamma_{#1}}
\newcommand{\isext}[2]{\delta_{#1 \ext #2}}
\newcommand{\ts}{{\graph}}
% When I introduce a new term or definition
\newcommand{\term}[1]{\textcolor{Mahogany}{\textbf{#1}}}
\newcommand{\tcdot}{} % Tentative cdot, not sure if I want to keep dots

% === Mathematical operators that are denoted with words ===
\newcommand{\setoperator}[1]{%
\expandafter\DeclareDocumentCommand\csname#1\endcsname{O{} O{} m}{{\mathsf{#1}_{##1}^{##2}}\br{##3}}%
}

\setoperator{Pa} % Parents of a node
\setoperator{Ch} % Children of a node
\setoperator{An} % Ancestry of a node
\setoperator{Sub} % subgraph
\setoperator{AnSub} % Ancestral subgraph
\setoperator{Ext} % Extension of outcomes
\setoperator{Com} % Compatible equivalence relation
\setoperator{Nec} % Necessary nodes
\setoperator{UnNec} % Unnecessary nodes
\setoperator{Inj} % injectable sets
\setoperator{ImInj} % images of the injectable sets
\setoperator{PreInj} % Pre-injectable sets
\setoperator{ImPreInj} % images of the Pre-injectable sets
\setoperator{Aut} % graph automorphism
\setoperator{Orb} % Group Orbits
\setoperator{Perm} % Permutation group
\newcommand{\PermM}[1]{\La_{#1}} % Permutation matrix
% \setoperator{Out} % Outcome space
\newcommand{\Events}[1]{\s{E}\br{#1}} % Set of events
\newcommand{\Dom}[1]{\s{D}\br{#1}} % Domian
% \setoperator{Dom} % Domian
% \setoperator{Dom} % Domian

\newcommand{\outc}[1]{o\bs{#1}} % Fritz's BBTII notation for observed outcomes
\DeclareDocumentCommand{\prob}{O{} O{}}{\ifthenelse{\equal{#1}{}}{P}{P_{#1}}\ifthenelse{\equal{#2}{}}{}{\br{#2}}} % probability distribution
\DeclareDocumentCommand{\probvec}{O{} O{}}{\ifthenelse{\equal{#1}{}}{\mathcal{P}}{\mathcal{P}_{#1}}\ifthenelse{\equal{#2}{}}{}{\br{#2}}} % probability distribution vector

% === Causal structure formatting for tikz ===
\input{../figures/causal_structures/formatting}

@@

                \scalebox{1.0}{\input{../figures/hypergraphs/minimal_example}}

@@

    \section{The Triangle Scenario}
    \label{sec:triangle_scenario}
    \begin{figure}
    \begin{center}
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../figures/causal_structures/triangle_scenario}}
            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
            \label{fig:triangle_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{0.8}{\input{../figures/causal_structures/inflated_triangle_scenario}}
            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
            \label{fig:inflated_triangle_scenario}
        \end{minipage}
    \end{center}
    \end{figure}

@@

    \begin{figure}
    \newlength\figureheight
    \newlength\figurewidth
    \setlength\figureheight{2.7in}
    \setlength\figurewidth{.48\textwidth}
    \begin{center}
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \includegraphics{../figures/CHSH_convex.pdf}
            \caption{Convex optimizations against $I\tsb{CHSH}$ recover algebraic violation of $4$.}
            \label{fig:CHSH_convex}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \includegraphics{../figures/CHSH_quantum.pdf}
            \caption{Quantum optimizations against $I\tsb{CHSH}$ recover maximum violation of $2\sqrt{2}$.}
            \label{fig:CHSH_quantum}
        \end{minipage}
    \end{center}
    \end{figure}

@@

    \subsection{Network Permutation Matrix}
    \begin{figure}
        \centering
        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../figures/perm_mtrx.pdf}
        \caption{The network permutation matrix $\netperm$ for $\br{\Hilb^2}^{\otimes 6}$ realized on the triangle scenario. Black represents a value of $1$ and $0$ otherwise.}
        \label{fig:perm_mtrx}
    \end{figure}
    Finally, we introduce the \term{network permutation matrix} $\netperm$ for the Triangle Scenario of \cref{fig:triangle_scenario}. For bipartite qubit states, $\netperm$ becomes a $64\times64$ bit-wise matrix that acts on the measurements $M$ and is depicted in \cref{fig:perm_mtrx}. To illuminate its necessity, consider \cref{eq:triangle_quantum_distributions} without $\netperm$.
    \begin{align*}
    \prob[ABC]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA}} \br{M^a_{A}\otimes M^b_{B} \otimes M^c_{C}}}\\
    &= \Tr\bs{\br{\rho_{AB}M^a_{A}}\otimes\br{\rho_{BC}M^b_{B}}\otimes\br{\rho_{CA}M^c_{C}}}\\
    &= \Tr\br{\rho_{AB}M^a_{A}}\Tr{\br{\rho_{BC}M^b_{B}}}\Tr{\br{\rho_{CA}M^c_{C}}}\\
    &= \prob[A\mid \rho_{AB}]\br{a}\prob[B\mid \rho_{BC}]\br{b}\prob[C\mid \rho_{CA}]\br{c}
    \end{align*}
    On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$. This is analogously troubling for $B$ and $C$ as well. The network permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$. To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
    \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
    $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''. It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
    \subsection{Degeneracy}
    \todo[TC]{Discuss local unitary degeneracy}
    \section{Convex Parametrization of Finite Probability Distributions}
    As discussed in \cref{sec:optimizations}, there is a need to parameterize the family of all probability distributions $\prob[V]$ over a given set of variables $V = \br{v_1, \ldots, v_{\abs{V}}}$. If the cardinality of $O_{V}$ is finite, then this computationally feasible. The space of probability distributions over $n = \abs{O_{V}}$ distinct outcomes forms a $n-1$ dimensional convex polytope naturally embedded in $\R_{\geq 0}^n$~\cite{Brunner_2013} that is parameterizable by $n-1$ real value parameters; normalization $\sum_{o\bs{V} \in O_V} \prob[V][\outc{V}] = 1$ accounts for the `$-1$'. An example of a non-degenerate parameterization of $\prob[V]$ consists of $n-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{n-1}}, \lambda_i \in \bs{0, \pi/2}$ which generate the $n$ probability values $p_j$ using hyperspherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary},
    \begin{equation}
    \begin{gathered}
        \label{eq:convex_param}
        p_j = \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1 \\
        p_n = \prod_{i=1}^{n-1} \sin^2 \lambda_i
    \end{gathered}
    \end{equation}
    Furthermore due to the periodicity of the parameter space $\lambda$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems. For continuity reasons, unconstrained optimizations are performed whenever possible.

@@

    \bibliography{references}
\end{document}

>>>>

% === All of the Packages I use frequently ===
\usepackage{../../packages/document_config}
\usepackage{../../packages/shared}
\usepackage{../../packages/misc_commands}

% === Causal structure formatting for tikz ===
\input{../../figures/causal_structures/formatting}

@@

                \scalebox{1.0}{\input{../../figures/hypergraphs/minimal_example}}

@@

    \section{The Triangle Scenario}
    \label{sec:triangle_scenario}
    \begin{figure}
    \begin{center}
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{1.0}{\input{../../figures/causal_structures/triangle_scenario}}
            \caption{The casual structure of the Triangle Scenario. Three variables $A,B,C$ are observable and illustrated as triangles, while $X, Y, Z$ are latent variables illustrated as circles.}
            \label{fig:triangle_scenario}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \scalebox{0.8}{\input{../../figures/causal_structures/inflated_triangle_scenario}}
            \caption{An inflated causal structure of the Triangle Scenario \cref{fig:triangle_scenario}.}
            \label{fig:inflated_triangle_scenario}
        \end{minipage}
    \end{center}
    \end{figure}

@@

    \begin{figure}
    \newlength\figureheight
    \newlength\figurewidth
    \setlength\figureheight{2.7in}
    \setlength\figurewidth{.48\textwidth}
    \begin{center}
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \includegraphics{../../figures/CHSH_convex.pdf}
            \caption{Convex optimizations against $I\tsb{CHSH}$ recover algebraic violation of $4$.}
            \label{fig:CHSH_convex}
        \end{minipage}\hspace{0.04\textwidth}%
        \begin{minipage}[b]{.48\textwidth}
            \centering
            \includegraphics{../../figures/CHSH_quantum.pdf}
            \caption{Quantum optimizations against $I\tsb{CHSH}$ recover maximum violation of $2\sqrt{2}$.}
            \label{fig:CHSH_quantum}
        \end{minipage}
    \end{center}
    \end{figure}

@@

    \subsection{Network Permutation Matrix}
    \begin{figure}
        \centering
        \includegraphics[trim={1cm 1.2cm 1.0cm 1cm},clip,width=0.4\textwidth]{../../figures/perm_mtrx.pdf}
        \caption{The network permutation matrix $\netperm$ for $\br{\Hilb^2}^{\otimes 6}$ realized on the triangle scenario. Black represents a value of $1$ and $0$ otherwise.}
        \label{fig:perm_mtrx}
    \end{figure}
    Finally, we introduce the \term{network permutation matrix} $\netperm$ for the Triangle Scenario of \cref{fig:triangle_scenario}. For bipartite qubit states, $\netperm$ becomes a $64\times64$ bit-wise matrix that acts on the measurements $M$ and is depicted in \cref{fig:perm_mtrx}. To illuminate its necessity, consider \cref{eq:triangle_quantum_distributions} without $\netperm$.
    \begin{align*}
    \prob[ABC]\br{abc} &\stackrel{?}{=} \Tr\bs{\br{\rho_{AB}\otimes\rho_{BC}\otimes\rho_{CA}} \br{M^a_{A}\otimes M^b_{B} \otimes M^c_{C}}}\\
    &= \Tr\bs{\br{\rho_{AB}M^a_{A}}\otimes\br{\rho_{BC}M^b_{B}}\otimes\br{\rho_{CA}M^c_{C}}}\\
    &= \Tr\br{\rho_{AB}M^a_{A}}\Tr{\br{\rho_{BC}M^b_{B}}}\Tr{\br{\rho_{CA}M^c_{C}}}\\
    &= \prob[A\mid \rho_{AB}]\br{a}\prob[B\mid \rho_{BC}]\br{b}\prob[C\mid \rho_{CA}]\br{c}
    \end{align*}
    On an operational level, this corresponds to $A$ making a measurement on \textit{both} subsystems of $\rho_{AB}$ and \textit{not} on any component of $\rho_{CA}$. This is analogously troubling for $B$ and $C$ as well. The network permutation matrix $\netperm$ corresponds to \textit{aligning} the underlying $6$-qubit joint state $\rho$ with the joint measurement $M$. To understand its effect, consider its effect on $6$-qubit pure state $\ket{q_1} \otimes \cdots \otimes \ket{q_6} = \ket{q_1q_2q_3q_4q_5q_6}$ where $\forall i : \ket{q_i} \in \Hilb^2$.
    \[ \netperm\ket{q_1q_2q_3q_4q_5q_6} = \ket{q_2q_3q_4q_5q_6q_1} \]
    $\netperm$ acts as a \textit{partial transpose} on $\br{\Hilb^2}^{\otimes 6}$ by shifting the underlying tensor structure one subsystem to the ``left''. It is uniquely defined by its action on all $2^6$ orthonormal basis elements of $\br{\Hilb^2}^{\otimes 6}$,
    \[ \netperm \defined \sum_{\ket{q_i} \in \bc{\ket{0}, \ket{1}}}\ket{q_2q_3q_4q_5q_6q_1}\bra{q_1q_2q_3q_4q_5q_6} \]
    \subsection{Degeneracy}
    \todo[TC]{Discuss local unitary degeneracy}
    \section{Convex Parametrization of Finite Probability Distributions}
    As discussed in \cref{sec:optimizations}, there is a need to parameterize the family of all probability distributions $\prob[V]$ over a given set of variables $V = \br{v_1, \ldots, v_{\abs{V}}}$. If the cardinality of $O_{V}$ is finite, then this computationally feasible. The space of probability distributions over $n = \abs{O_{V}}$ distinct outcomes forms a $n-1$ dimensional convex polytope naturally embedded in $\R_{\geq 0}^n$~\cite{Brunner_2013} that is parameterizable by $n-1$ real value parameters; normalization $\sum_{o\bs{V} \in O_V} \prob[V][\outc{V}] = 1$ accounts for the `$-1$'. An example of a non-degenerate parameterization of $\prob[V]$ consists of $n-1$ parameters $\lambda = \br{\lambda_1, \ldots, \lambda_{n-1}}, \lambda_i \in \bs{0, \pi/2}$ which generate the $n$ probability values $p_j$ using hyperspherical coordinates~\cite{Hedemann_2013, Spengler_2010_Unitary},
    \begin{equation}
    \begin{gathered}
        \label{eq:convex_param}
        p_j = \cos^2 \lambda_j \prod_{i=1}^{j-1} \sin^2 \lambda_i \quad \forall j \in 1, \ldots, n - 1 \\
        p_n = \prod_{i=1}^{n-1} \sin^2 \lambda_i
    \end{gathered}
    \end{equation}
    Furthermore due to the periodicity of the parameter space $\lambda$, \cref{eq:convex_param} can be used for either constrained or unconstrained optimization problems. For continuity reasons, unconstrained optimizations are performed whenever possible.

@@

    \bibliography{../references}
\end{document}
